Towards human Super EEG

### 2018-10-02 paper/main.tex
minor paper organization stuff

\author
{Lucy L. W. Owen$^{1}$, Andrew C. Heusser$^{1}$, and Jeremy R. Manning$^{1\ast}$\\
\\
\normalsize{$^{1}$Department of Psychological and Brain Sciences,
  Dartmouth College,}\\
\normalsize{Hanover, NH 03755, USA}
}

@@

We also wondered whether reconstruction quality (measured as the
correlation between the observed and reconstructed data) varied with
the electrode locations (Fig.~\ref{fig:corrmap}B \& D). In general, reconstruction quality remained high throughout the brain. Although reconstruction accuracy appeared high in the medial temporal lobe, which is a common epileptic focus (and therefore a common target for electrode implantation), we observed a weak but statistically reliable negative correlation between reconstruction quality and electrode density (defined as the proportion of electrodes within 20 MNI units for each location; dataset 1: $r = -0.07, p < 10^{-5}$, dataset 2: $r = -0.16, p < 10^{-10}$). This provides some evidence that our reconstruction accuracy results cannot be driven only by volume conductance.  Qualitatively, it appeared that the distribution of electrodes was similar across the datasets, suggesting potential commonalities of target locations across patients and similarities in surgical decisions. Indeed, we found a relatively strong correlation between the electrode densities within the two datasets (defined as the proportion of electrodes within 20 MNI units for each 34686 voxels (Fig.~\ref{fig:density}A & B); $r = 0.57, p < 10^{-10}$).

@@

In addition to exploring how reconstruction quality varies with
location, we also wondered whether there might be effects of electrode
placements on reconstruction quality.  For example, are there
particular implantation locations that yield especially high
reconstruction accuracies at other locations throughout the brain? To gain insights into this questions, we computed the average reconstruction correlation for each patient, then computed the average patient reconstruction correlation for any patients who had electrodes within a 20 MNI unit diameter sphere centered on each voxel location. The resulting maps highlight the locations of implanted electrodes from patients whose
reconstructions were especially accurate  (Fig.~\ref{fig:informap}A & B). We found that the most informative locations were consistent across datasets which lends support to the notion that different electrode location are more informative about activity across patients (Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).  The locations in dark red might therefore be good candidate
implantation targets for neurosurgeons and neurologists who wish to
use Super EEG to reconstruct full-brain electrophysiological signals.
The above findings, that one can infer brain activity throughout a person's brain 
using recordings from a limited number of locations from that person's brain in conjunction with recordings from other people's brains, have deep
implications for the structure of brain data.  The first implication
is that the correlational structure of different people's brain data
is largely preserved across individuals. Despite recent evidence that different people have stable but reliably different resting state connectome~\cite{FinnEtal15}, our results suggest that the correlational structure of different people's brain data is preserved enough across individuals to provide meaningful information.

@@

\bibliography{memlab}
\bibliographystyle{Science}

>>>>

\author
{Lucy L. W. Owen$^{1}$, Andrew C. Heusser$^{1, 2}$, and Jeremy R. Manning$^{1\ast}$\\\\
$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
Hanover, NH 03755, USA\\
$^{2}$Akili Interactive,\\
Boston, MA 02110, USA}

@@

We also wondered whether reconstruction quality (measured as the
correlation between the observed and reconstructed data) varied with
the electrode locations (Fig.~\ref{fig:corrmap}B \& D). In general, reconstruction quality remained high throughout the brain. Although reconstruction accuracy appeared high in the medial temporal lobe, which is a common epileptic focus (and therefore a common target for electrode implantation), we observed a weak but statistically reliable negative correlation between reconstruction quality and electrode density (defined as the proportion of electrodes within 20 MNI units for each location; dataset 1: $r = -0.07, p < 10^{-5}$, dataset 2: $r = -0.16, p < 10^{-10}$). This provides some evidence that our reconstruction accuracy results cannot be driven only by volume conductance.  Qualitatively, it appeared that the distribution of electrodes was similar across the datasets, suggesting potential commonalities of target locations across patients and similarities in surgical decisions. Indeed, we found a relatively strong correlation between the electrode densities within the two datasets (defined as the proportion of electrodes within 20 MNI units for each 34686 voxels (Fig.~\ref{fig:density}A, B); $r = 0.57, p < 10^{-10}$).

@@

In addition to exploring how reconstruction quality varies with
location, we also wondered whether there might be effects of electrode
placements on reconstruction quality.  For example, are there
particular implantation locations that yield especially high
reconstruction accuracies at other locations throughout the brain? To gain insights into this questions, we computed the average reconstruction correlation for each patient, then computed the average patient reconstruction correlation for any patients who had electrodes within a 20 MNI unit diameter sphere centered on each voxel location. The resulting maps highlight the locations of implanted electrodes from patients whose
reconstructions were especially accurate  (Fig.~\ref{fig:informap}A and B). We found that the most informative locations were consistent across datasets which lends support to the notion that different electrode location are more informative about activity across patients (Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).  The locations in dark red might therefore be good candidate
implantation targets for neurosurgeons and neurologists who wish to
use Super EEG to reconstruct full-brain electrophysiological signals.
The above findings, that one can infer brain activity throughout a person's brain 
using recordings from a limited number of locations from that person's brain in conjunction with recordings from other people's brains, have deep
implications for the structure of brain data.  The first implication
is that the correlational structure of different people's brain data
is largely preserved across individuals. Despite recent evidence that different people have stable but reliably different resting state connectome~\cite{FinnEtal15}, our results suggest that the correlational structure of different people's brain data is preserved enough across individuals to provide meaningful information.

@@

\bibliography{CDL-bibliography/memlab.bib}
\bibliographystyle{Science}
